The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2018-09-14 revision/reviews.tex
update Andi 14_09_2018(1)
update Andi 14_09_2018(1)

\answerfin{The g-weight is the name of a variance estimator for the point estimate in eq.2 as opposed to another possible variance estimator here named the external estimator.  The origin of the g-weight name is more obvious in the citation provided in the same paragraph.  The g-weight is analogous to a hat matrix and can be extracted from the more compact form that was included in the article.  It the spirit of not being too verbose we chose the compact form. }
% --------------------------- %

@@

\answerfin{The extended synthetic estimator does not necessarily need to implement an ancova model.  That depends on the types of variables that the user has specified.  The extended synthetic estimator merely adds an indicator variable for the small area in addition to the other variables that the user specified.}
% --------------------------- %

@@

\answerfin{The term is consistent with much of the already published literature included in the citations.}
% --------------------------- %

@@

\answerfin{The "survey" package is in the finite population approach (aka list sampling).  It is mentioned on page 2.}
% --------------------------- %

>>>>

\answerfin{The g-weight is the name of a variance estimator for the point estimate in eq.2 as opposed to another possible variance estimator here named the external estimator.  The origin of the g-weight name is more obvious in the citation provided in the same paragraph.  The g-weight is analogous to a hat matrix and can be extracted from the more compact form that was included in the article. In the spirit of not being too verbose we chose the compact form. }
% --------------------------- %

@@

\answerfin{The extended synthetic estimator does not necessarily need to implement an ancova model.  That depends on the types of variables that the user has specified.  The extended synthetic estimator merely adds an indicator variable for the small area in addition to the other variables that the user specified. This can in fact extend the model to an ancova model if the explanatory variables contain at least one continuous predictor. However, the reason of adding the indicator variable exclusively is to ensure the zero-mean-residual property in both the global domain F and small area G, and not to improve the model fit. We think that linking the indicator variable to the anova or ancova modeling technique might probably cause misunderstanding of the indicator purpose on the side of the readers.}
% --------------------------- %

@@

\answerfin{The term is consistent with much of the already published literature included in the citations (e.g., von L{\"u}pke et al. 2012).}
% --------------------------- %

@@

\answerfin{The \textit{survey} package is in the finite population approach (aka list sampling).  It is mentioned on page 2.}
% --------------------------- %

### 2018-09-14 rnw/Introduction.Rnw
update Andi 14_09_2018(1)
update Andi 14_09_2018(1)

Multistage and multiphase estimation has already been implemented in commercial as well as open-source software, such as the survey sampling procedures in \proglang{SAS} \citep{sas} and the \pkg{survey} package in \proglang{R} \citep{survey}. However, both are targeted towards list-sampling as it is applied in official statistics. Available software providing multiphase sampling methods better suited for forest inventories has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} and the \pkg{maSAE} package by \citet{cullmann2016}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available, which is the motivation behind the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2017a}. The implemented estimators cover 32 inventory scenarios and can be used for post-stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.

>>>>

Multistage and multiphase estimation has already been implemented in commercial as well as open-source software, such as the survey sampling procedures in \proglang{SAS} \citep{sas} and the \pkg{survey} package in \proglang{R} \citep{survey}. However, both are targeted towards list-sampling as it is applied in official statistics. Available software providing multiphase sampling methods better suited for forest inventories has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} and the \pkg{maSAE} package by \citet{cullmann2016}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available, which is the motivation behind the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2018b}. The implemented estimators cover 32 inventory scenarios and can be used for post-stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.
